Research Notes

### 2019-02-03 writeups/notes.tex
update analytical fit function

The model we're examining now is if part of the flow has synchronized to the
horizontal phase velocity of the wave. Then as the wavetrain is incident on the
wave with horizontal momentum flux $S_{px}$, it completely deposits its
horizonttal momentum. Thus, $S_{px}$ goes from the wave's, which is well known,
down to zero, being deposited into the mean flow, which forces
\begin{equation}
    \rho(z) c_{ph,x} \pd{z_c}{t} = -S_{px}.
\end{equation}
where $c_{ph, x}$ is the horizontal phase velocity/critical velocity, $z_c$ is
the location of the dissipation front, and $S_{px}$ constant is the incident
momentum flux. This can be analytically solved if we take $\rho(z) \approx
\rho_0 \propto e^{-z/H}$. Try ansatz $z(t) = -H\p*{\ln t + \ln \tau}$ and we
find
\begin{equation}
    z(t) = -H\ln t - H\ln \frac{H\rho_0(z = 0)c_{ph, x}}{S_{px}}.
\end{equation}

>>>>

The model we're examining now is if part of the flow has synchronized to the
horizontal phase velocity of the wave. Then as the wavetrain is incident on the
wave with horizontal momentum flux $S_{px}$, it completely deposits its
horizonttal momentum. Thus, $S_{px}$ goes from the wave's, which is well known,
down to zero, being deposited into the mean flow, which forces
\begin{equation}
    \rho(z) c_{ph,x} \pd{z_c}{t} = -S_{px}.
\end{equation}
where $c_{ph, x}$ is the horizontal phase velocity/critical velocity, $z_c$ is
the location of the dissipation front, and $S_{px}$ constant is the incident
momentum flux. This can be analytically solved if we take $\rho(z) \approx
\rho_0 \propto e^{-z/H}$. Try ansatz $z(t) = -H\p*{\ln t / \tau}$ and we
find
\begin{align}
    \rho_0(z = 0) \frac{t}{\tau} c_{ph, x} \p*{-\frac{H}{t}} &= -S_{px}
        \nonumber\\
    \tau &= \frac{H\rho_0(z = 0)c_{ph, x}}{S_{px}},\nonumber\\
    z(t) &= -H\ln \frac{t + t_0}{\tau}.
\end{align}
$t_0$ is some constant of integration that is fit by setting $z_c(t = 0) = z_0$
some initial condition. Let's first notice that $z(-t_0) = +\infty, z(\tau -
t_0) = 0$, and so $\tau$ corresponds to the time it takes to spin up the entire
atmosphere above $z = 0$. Indeed, halving $S_{px}$ doubles the amount of time
necessary.

In our simulations, it seems like $S_{px}$ decreases over time due to reflective
behavior setting in (similar to Winters \& d'Asaro, though since they had a very
narrow critical layer they observed transmission too, impossible in our case).
We can thus consider how two $z(t, S_{px})$ solutions differ based on choice of
$S_{px}$ given some fixed initial condition. In our case, since the beginning of
the simulation is dominated by transients, horizontal momentum dissipation and
formation of the critical layer, our equation is only really valid towards the
end of the simulation. Thus, we formulate our problem as follows: given two
$S_{px}, \alpha S_{px}$, compute $z(t)$ for both given initial condition
$z(t_f) = z_f$. We can solve and obtain
\begin{equation}
    t_0 = \tau e^{-z_f/H} - t_f,
\end{equation}
and so the exact solution becomes
\begin{equation}
    z(t) = -H\ln \frac{t - t_f + \tau e^{-z_f/H}}{\tau}.
\end{equation}
